Analysis-ready VCF at Biobank scale using Zarr

### 2025-03-31 paper.tex
More updates

\section{Availability of source code and requirements}
\subsection{GitHub repository vcf-zarr-spec}
\begin{description}
\item[Project name:]  vcf-zarr-spec
\item[Github link:] https://github.com/sgkit-dev/vcf-zarr-spec/
\item[Operating system(s):] Platform independent
\item[Programming language:] NA
\item[License:] Apache-2.0
\item[Software Heritage PID:]
swh:1:snp:9f25395ea05afd4fc29912dcbf0e21d879f5cfee \cite{vcfzarr-spec-swh}
\end{description}

% \end{itemize}

>>>>

\section{Availability of source code and requirements}
\subsection{GitHub repository vcf-zarr-spec}
\begin{description}
\item[Project name:]  vcf-zarr-spec
\item[Github link:] \url{https://github.com/sgkit-dev/vcf-zarr-spec/}
\item[Operating system(s):] Platform independent
\item[Programming language:] NA
\item[License:] Apache-2.0
\item[Software Heritage PID:]
swh:1:snp:9f25395ea05afd4fc29912dcbf0e21d879f5cfee \cite{vcfzarr-spec-swh}
\end{description}

\subsection{GitHub repository vcf-zarr-publication}
\begin{description}
\item[Project name:]  vcf-zarr-publication
\item[Github link:] \url{https://github.com/sgkit-dev/vcf-zarr-publication/}
\item[Operating system(s):] Platform independent
\item[Programming language:] Python
\item[License:] CC-BY (manuscript), Apache-2.0 (codes), CC0 (data)
\item[Software Heritage PID:]
swh:1:snp:da8d16ddcf9ee9ede198001414fe15e18eb4042f \cite{vcfzarr-pub-swh}
\end{description}

\subsection{GitHub repository bio2zarr}
\begin{description}
\item[Project name:]  bio2zarr
\item[Github link:] \url{https://github.com/sgkit-dev/bio2zarr/}
\item[Operating system(s):] Platform independent
\item[Programming language:] Python
\item[License:] Apache-2.0
\item[Software Heritage PID:]
swh:1:snp:367cd22bac0e7120869f081f3a216caa9fe4af1d \cite{bio2zarr-swh}
\item[RRID:] SCR\_026481
\item[Bio.tools Unique Identifier:] bio2zarr
\end{description}

% 3. GitHub repository bio2zarr
% Project name:  bio2zarr
% Github link: https://github.com/sgkit-dev/bio2zarr/
% Python module: https://pypi.org/project/bio2zarr/
% Operating system(s): Platform independent
% Programming language: Python
% License: Apache-2.0
% Software Heritage PID: [207]
